Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-03 manuscript/paper-tycho.tex
Update ms tables/plts, spectr disc, specvar ipynb
Manuscript table/plots generated for regions-6
Add text on srcutlog fits, spectral variation tests, sketch out
radio profile fitting / shape analysis.
Split spectral variation code to new ipynb (not tested)
Rename fitting ipynbs more usefully, clean radio prf fitting ipynb

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
relatively strong synchrotron radiation, in conjunction with multiwavelength
spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
suggests that electrons are accelerated to PeV energies in young SNRs.
Although synchrotron emission due to accelerated electrons does not imply
acceleration of an unseen hadronic component, the prevailing theory of
diffusive shock acceleration (DSA) should operate on both protons and
electrons.  Efficient hadron acceleration in supernova remnant shocks is a
prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
``knee'' \citep{vink2012}.

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.  Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

% What makes these shock rims?
The widths of these X-ray rims are controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped
downstream of the shock, so that electrons may not radiate as efficiently and
thin rims reflect the spatial structure of the field rather than efficient
particle acceleration (and losses) and/or efficient synchrotron cooling
\citep{pohl2005}.

% Whatever makes these shock rims also imposes energy dependence
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  In the limiting case of constant magnetic field and
negligible particle diffusion, the rims are said to be synchrotron loss-limited
and rim widths should narrow with increasing photon frequency $\nu$ as
$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
higher energies, yielding a slower drop-off in rim widths when diffusion
dominates.  Magnetic damping, if at a length scale comparable to filament
widths, also favors more energy-insensitive rim widths -- intuitively, if the
magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.

% Magnetic damping?
Magnetic damping immediately behind the shock offers a tantalizing alternative
explanation for filament rims that requires less extreme magnetic field
amplification, and the possibility of damping in SNR shocks has not been fully
tested \citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined
radio and X-ray synchrotron rim profiles, but found that neither damping nor
synchrotron losses matched radio profiles particularly well.  \citet{araya2010}
measured rims at multiple energy bands in Cas A, but suggested that the rims
only narrow more weakly than expected and did not consider magnetic damping.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the expectation is that
damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
further extended the idea of discriminating between damped or loss-limited
rims by measuring rim width energy dependence in X-ray energies and found that
rims consistently narrowed in the remnant of SN 1006.

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citep{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
Furthermore, Tycho has been a prime target of study for determining whether
hadrons are being accelerated in historic SNRs \citep[and references
therein]{morlino2012}; understanding the acceleration process will also bear
upon our understanding of CR acceleration in Tycho.

@@

All constants and equations are given in CGS (Gaussian) units.  Our
presentation is somewhat abbreviated, but a fuller exposition and literature
review is given by \citetalias{ressler2014}.

@@

% e- cutoff energy result
With a diffusion coefficient in hand, we may determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated to higher energies and the energy spectrum drops off steeply.  The
cut-off energy is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
shock with compression ratio 4 and isotropic magnetic turbulence on both sides
of the shock.

% srcut constraint on diffusion
As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(100 \muG\right)
        \left(2657 \unit{erg^2}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but, recall that the specific electron energies associated
with $\eta_2$ will depend on $B$).

@@

The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
rettig2012} assume $D(x) B^2(x)$ constant in order to make the equation
semi-analytically tractable.  Although unphysical, we enforce this criterion by
using a modified diffusion coefficient in our calculations following
\citet{rettig2012}, given as:
\begin{equation} \label{eq:ddamp}
    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
             \left[ \frac{\Bmin}{B_0} +
                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
\end{equation}
This does strengthens the spatial-dependence of the diffusion coefficient, as
compared to the expected $D(x) \propto 1/B(x)$.
\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
will check shortly}

@@

% Intuition: how damping affects rim widths
We expect magnetic damping to produce comparatively energy-independent rim
widths.  If synchrotron rim widths are set by magnetic damping
at some observation energy, then the rims must be damped at all lower
observation energies as well.  Then rim widths will be relatively constant
(small $|\mE|$) below a threshold energy and may decrease, or even increase
(if $\mu > 1$) once advection or diffusion become dominant controls on rim
widths at higher photon energies (advection: $l_\mt{ad} < a_b$;
diffusion: $a_b < l_{\mt{diff}} < l_{\mt{ad}}$).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        %\plotone{figures/f0-snr-inv.png}
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \note[Aaron]{Inverted colors for draft only}
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

% Downstream spectra and numbers
% NOTE keep stated ranges, region numbers up to date
% THIS IGNORES THE BAD (insufficient counts) REGION 19 DOWNSTREAM SPECTRUM FIT (!!)
Downstream spectra are generally poorly-fit by the absorbed power law model,
reflecting thermal contamination from \ion{Si}{13} and \ion{S}{15} He$\alpha$
line emission at $1.85$ and $2.45$ keV.  To confirm that thermal emission is
dominated by these two lines near the shock, we also performed fits with (1)
both lines excised ($1.7$--$2.0 \unit{keV}$, $2.3$--$2.6 \unit{keV}$ counts
removed) and (2) with both lines fitted to Gaussian profiles.  Fits with lines
excised yield $\chi^2_{\mt{red}}$ values between $0.8$--$1.4$, excepting only
Regions 5 and 20 with $\chi^2_{\mt{red}} \sim 1.8$ due to the presence of
additional thermal lines.  Fits with lines fitted to Gaussian profiles yield
$\chi^2_{\mt{red}}$ values $0.83$--$1.22$, again excepting Regions 5, 20 which
have $\chi^2_{\mt{red}} \sim 1.6$.  In both fits (lines excised or modeled), we
find somewhat smaller best fit column densities ($0.32$--$0.74 \times 10^{22}
\unit{cm^{-1}}$) but similar best fit photon indices ($2.52$--$3.05$), compared
to those of the rim spectra.  The consistent photon indices confirm that the
same synchrotron continuum may be recovered from beneath thermal line emission.

@@

\begin{table*}
    \scriptsize
    \centering
    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
    \input{suppl-spec-pt2.tex}
    \tablecomments{As described in text,
    we consider absorbed power law fits with lines fitted to two Gaussians
    (here characterized by equivalent width and line energy), or with lines
    manually excised.  See comments on Table~\ref{tab:spec}.}
\end{table*}

% This table is still useful to look at the fit parameters (to make
% qualitative statements about excised/Gaussian line fit quality,
% or to send around to collaborators)
%\begin{table*}
%    \footnotesize
%    \centering
%    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
%    \input{tab-spec-pt2.tex}
%\end{table*}

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Errors in our least squares fits average
the positive and negative errors on each FWHM measurement.  For an input set of
model parameters, we numerically computed intensity profiles and hence model
FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters
(subject to varied constraints on model parameters in the following paragraph).
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
Errors on best fit parameters were computed by varying each fit parameter and
obtaining a new best fit model, with one less degree of freedom, to find the
parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

% How we twiddled model knobs
We first considered a purely loss-limited model (constant magnetic field
$B_0$) with three parameters $\mu$, $\eta_2$, and $B_0$.  To make nonlinear
fitting tractable, we fixed $\mu$ in all fits and considered $\mu = 0$, $1/3$,
$1/2$, $1$, $1.5$, and $2$.  In particular, nonlinear diffusion-energy
scalings with $\mu = 1/3$ and $1/2$ may arise from Kolmogorov and Kraichnan
turbulent energy spectra respectively \citep{reynolds2004}.  The remaining
parameters $\eta_2$ and $B_0$ varied freely.

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We fixed $a_b$ at $14$ different values between $0.5$ and $0.002$ (sampling
most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
free.  Formally, we do not seek a best fit value of damping length $a_b$, so
our ``best'' damping fits report the value of $a_b$ yielding the smallest
$\chi^2$ value.  Finally, we fixed $\mu = 1$ for all damped fits.

% Variants on our fitting procedure
To better explore the parameter space of model predictions, we also computed
model fits with both $\eta_2 = 1$ and $\mu = 1$ fixed for both scenarios of
constant and damped magnetic field.  We also attempted damping fits with
$\Bmin = 2 \muG$, somewhat on the lower end of estimated galactic
magnetic field values.

@@

% Model resolution error
As the full model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals (discretization over
radial coordinate, line-of-sight coordinate, electron distribution, Green's
function integrals).  We chose integration resolutions such that the
fractional error in model FWHMs associated with halving or doubling each
integration resolution (individually) is less than $1\%$ for the parameter
space relevant to our filaments -- $\eta_2 \leq 10^3$ for the loss-limited
model and $\eta_2 \leq 10$ for the magnetic damping model).  In our error
analysis, the maximum resolution errors in a sample of parameter space are
typically $0.1$--$1\%$, but mean and median errors are typically an order of
magnitude smaller that maximum errors.  Thus we expect numerical errors to be
negligible.

@@

% Present table of FWHM results
Table~\ref{tab:fwhms} reports FWHM measurements for all of our regions.
We also report $\mE$ values for all but the lowest energy band, computed
point-to-point between discrete energy bands as:
\begin{equation}
    \mE(E_2) = \frac{\ln(w_2/w_1)}{\ln(E_2/E_1)}
\end{equation}
where $w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each
energy band -- e.g., $\mE$ at $1 \unit{keV}$ is computed using FWHMs from
$0.7$--$1 \unit{keV}$ and $1$--$1.7 \unit{keV}$, with $E_2 = 1 \unit{keV}$ and
$E_1 = 0.7 \unit{keV}$.  Errors on $\mE$ are propagated in quadrature from
adjacent FWHM measurements.

@@

% Observations of mE and rim widths and stuff
Measured rim widths decrease with energy in most regions and energy bands.
Although the measurement scatter is quite large, shown dramatically in the
point-wise computed $\mE$ values, the mean rim width decreases consistently
with increasing energy.  Furthermore, mean $\mE$ values are consistently
negative and tend smoothly towards $0$ (weaker energy-dependence) with
increasing energy.

% Errors in rim widths
The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
reflecting the high quality of underlying \Chandra data as also seen in
Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
part to (1) our profile fitting procedure, which depends on a somewhat
arbitrary choice of profile fit function, and (2) variation in Tycho's rim
morphology (see Figure~\ref{fig:profiles}).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.5}
    }{}
    \plotone{figures/prfs-fit-01.pdf} \\
    \plotone{figures/prfs-fit-16.pdf}
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Shaded
        regions on damped profiles indicate the damping ($e$-folding)
        lengthscale for the magnetic field.  Note that radial coordinate ($r$)
        axes agree in each row (same region), but not in each column.
    \label{fig:rims}}
\end{figure}

>>>>

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The strong
and time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
patnaude2007}, in conjunction with multiwavelength spectral modeling
\citep{aharonian2004, acero2010, ackermann2013}, suggests that electrons are
accelerated to PeV energies in young SNRs.  Although synchrotron emission due
to accelerated electrons does not imply acceleration of an unseen hadronic
component, the prevailing theory of diffusive shock acceleration (DSA) should
operate on both positive ions and electrons.  Efficient hadron acceleration in
supernova remnant shocks is a prime candidate source for galactic cosmic rays
up to the cosmic ray spectrum's ``knee'' \citep{vink2012}.

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, the synchrotron
spectrum of supernova remnants steepens at X-ray energies \citep{reynolds1999},
corresponding to a cut-off in the underlying electron spectrum as predicted by
diffusive shock acceleration \citep{webb1984}.  Many fundamental questions
about the shock acceleration process remain to be answered.  Under what
conditions do shocks accelerate particles efficiently?  How are magnetic fields
amplified in such shocks?  \citet{reynolds2008} reviews relevant observations
and open questions to date.  The answers to these questions are broadly
relevant to many astrophysical shocks, such as Earth's bow shock
\citep{ellison1990}, starburst galaxies \citep{heckman1990}, jets of active
galactic nuclei \citep{chen2014}, galaxy clusters \citep{van-weeren2010}, and
cosmological shocks \citep{ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

% What makes these shock rims?
The widths of these X-ray rims are controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped
downstream of the shock, preventing electrons from radiating efficiently so
that thin rims reflect the spatial structure of the field rather than efficient
particle acceleration and synchrotron cooling \citep{pohl2005}.

% Whatever makes these shock rims also imposes energy dependence
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  If the downstream magnetic field is constant and
diffusion is negligible downstream of the shock, the rims are said to be
synchrotron loss-limited and rim widths ($w$) should narrow with increasing
photon frequency ($\nu$) as $w \propto \nu^{-1/2}$. Diffusion smears out rims
at all energies with stronger effect at higher energies, yielding a slower
drop-off in rim widths when diffusion dominates.  Magnetic damping, if at a
length scale comparable to filament widths, also favors more energy-insensitive
rim widths -- intuitively, if the magnetic field turns off, synchrotron
radiation turns off regardless of electron energy.

% Magnetic damping?
Magnetic damping immediately behind the shock offers an alternative explanation
for filament rims that requires less extreme magnetic field amplification, and
the possibility of damping in SNR shocks has not been fully tested
\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined radio and
X-ray synchrotron rim profiles, but found that neither damping nor synchrotron
losses matched radio profiles particularly well.  \citet{araya2010} measured
rims at multiple energy bands in Cas A, but suggested that the rims only narrow
more weakly than expected and did not consider magnetic damping.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the expectation is that
damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
further extended the idea of discriminating between damped or loss-limited rims
by measuring rim width energy dependence in X-ray energies and found that rims
consistently narrowed in the remnant of SN 1006.

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citep{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) allows fine sampling of the remnant rims.  Furthermore, Tycho
is a prime target of study to determine whether hadrons are being accelerated
in historic SNRs \citep[and references therein]{morlino2012}; understanding the
acceleration process for electrons will also bear upon our understanding of CR
acceleration in Tycho.

@@

All constants and equations are given in CGS (Gaussian) units.  Our
presentation is somewhat abbreviated, but a fuller exposition and literature
review are given by \citetalias{ressler2014}.

@@

% e- cut-off energy result
With a diffusion coefficient in hand, we may determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated to higher energies and the energy spectrum drops off steeply.  The
cut-off energy is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
shock with compression ratio 4 and isotropic magnetic turbulence on both sides
of the shock.

% srcut constraint on diffusion
As the DSA imposed electron cut-off results in a cut-off on SNR synchrotron
flux, the synchrotron cut-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:cutoff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(100 \muG\right)
        \left(2657 \unit{erg^2}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but, recall that the specific electron energies associated
with $\eta_2$ will depend on $B$).

@@

The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
rettig2012} assume $D(x) B^2(x)$ constant in order to make
equation~\eqref{eq:model} semi-analytically tractable.  Although unphysical, we
enforce this criterion by using a modified diffusion coefficient in our
calculations following
\citet{rettig2012}, given as:
\begin{equation} \label{eq:ddamp}
    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
             \left[ \frac{\Bmin}{B_0} +
                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
\end{equation}
This strengthens the spatial-dependence of the diffusion coefficient, as
compared to the expected $D(x) \propto 1/B(x)$.
% TODO
%\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
%will check shortly}

@@

% Intuition: how damping affects rim widths
We expect magnetic damping to produce comparatively energy-independent rim
widths.  If synchrotron rim widths are set by magnetic damping
at some observation energy, then the rims must be damped at all lower
observation energies as well.  Then rim widths will be relatively constant
(small $|\mE|$) below a threshold energy and may decrease, or even increase
(if $\mu > 1$) once advection or diffusion become dominant controls on rim
widths at higher photon energies (advection: $l_\mt{ad} < a_b$;
diffusion: $l_{\mt{diff}} > l_{\mt{ad}}, a_b$).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        %\plotone{figures/f0-snr-inv.png}
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

% Downstream spectra and numbers
% NOTE keep stated ranges, region numbers up to date
Downstream spectra are generally poorly-fit by the absorbed power law model,
reflecting thermal contamination from \ion{Si}{13} and \ion{S}{15} He$\alpha$
line emission at $1.85$ and $2.45$ keV.  To confirm that thermal emission is
dominated by these two lines near the shock, we also performed fits with (1)
both lines excised ($1.7$--$2.0 \unit{keV}$, $2.3$--$2.6 \unit{keV}$ counts
removed) and (2) with both lines fitted to Gaussian profiles.  Fits with lines
excised yield $\chi^2_{\mt{red}}$ values between $1$--$5$.  Fits with lines
fitted to Gaussian profiles yield $\chi^2_{\mt{red}}$ values $0.83$--$1.6$.  In
both fits (lines excised or modeled), we find somewhat smaller best fit column
densities ($0.3$--$0.8 \times 10^{22} \unit{cm^{-1}}$) but similar best fit
photon indices ($2.6$--$3.1$), compared to those of the rim spectra.  The
consistent photon indices indicate that the same synchrotron continuum is
present beneath thermal line emission.

@@

% This table is still useful to look at the fit parameters (to make
% qualitative statements about excised/Gaussian line fit quality,
% or to send around to collaborators)
%\begin{table*}
%    \scriptsize
%    \centering
%    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
%    \input{suppl-spec-pt2.tex}
%    \tablecomments{As described in text,
%    we consider absorbed power law fits with lines fitted to two Gaussians
%    (here characterized by equivalent width and line energy), or with lines
%    manually excised.  See comments on Table~\ref{tab:spec}.}
%\end{table*}

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
average the positive and negative errors on each FWHM measurement.  For an
input set of model parameters, we numerically computed intensity profiles and
hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters.
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
Errors on best fit parameters were computed by varying each fit parameter and
obtaining a new best fit model, with one less degree of freedom, to find the
parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

% How we twiddled model knobs
We first considered a purely loss-limited model (constant downstream magnetic
field $B_0$) with three parameters $\mu$, $\eta_2$, and $B_0$.  To make
nonlinear fitting tractable, we fixed $\mu$ in all fits and considered $\mu =
0$, $1/3$, $1/2$, $1$, $1.5$, and $2$.  In particular, nonlinear
diffusion-energy scalings with $\mu = 1/3$ and $1/2$ may arise from Kolmogorov
and Kraichnan turbulent energy spectra respectively \citep{reynolds2004}.  The
remaining parameters $\eta_2$ and $B_0$ varied freely.

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We fixed $a_b$ at $14$ different values between $0.5$ and $0.002$ (sampling
most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
free.  Formally, we do not seek a best fit value of damping length $a_b$, so
our ``best'' damping fits report the value of $a_b$ yielding the smallest
$\chi^2$ value.  Finally, $\mu = 1$ was fixed for all damped fits.

@@

% Model resolution error
Predicted rim widths are subject to resolution error in the numerical integrals
(discretization over radial coordinate, line-of-sight coordinate, electron
distribution, Green's function integrals).  We chose integration resolutions
such that the fractional error in model FWHMs associated with halving or
doubling each integration resolution is less than $1\%$ for the parameter space
relevant to our filaments.  In our error analysis, the maximum resolution
errors in a sample of parameter space are typically $0.1$--$1\%$, but mean and
median errors are typically an order of magnitude smaller that maximum errors.

@@

% Present table of FWHM results
Measured rim widths decrease with energy in most regions and energy bands.
Table~\ref{tab:fwhms} reports FWHM measurements for all of our regions.
We also report $\mE$ values for all but the lowest energy band, computed
point-to-point between discrete energy bands as:
\begin{equation}
    \mE(E_2) = \frac{\ln(w_2/w_1)}{\ln(E_2/E_1)}
\end{equation}
where $w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each
energy band -- e.g., $\mE$ at $1 \unit{keV}$ is computed using FWHMs from
$0.7$--$1 \unit{keV}$ and $1$--$1.7 \unit{keV}$, with $E_2 = 1 \unit{keV}$ and
$E_1 = 0.7 \unit{keV}$.  Errors on $\mE$ are propagated in quadrature from
adjacent FWHM measurements.

@@

% Observations of mE and rim widths, errors
Although the measurement scatter is quite large, shown dramatically in the
point-wise computed $\mE$ values, the mean rim width decreases consistently
with increasing energy.  Furthermore, mean $\mE$ values are consistently
negative and tend smoothly towards $0$ (weaker energy-dependence) with
increasing energy.  The errors on FWHM measurements are typically $\abt 10\%$
or smaller, reflecting the high quality \Chandra data as also seen in
Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
part to (1) our profile fitting procedure, which depends on a somewhat
arbitrary choice of profile fit function, and (2) variation in Tycho's rim
morphology (e.g., Figure~\ref{fig:profiles}).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.5}
    }{}
    \plotone{figures/prfs-fit-01.pdf} \\
    \plotone{figures/prfs-fit-16.pdf}
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
        damped profiles indicate the magnetic field damping lengthscale $a_b$.
        \label{fig:rims}}
\end{figure}
